Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-06 paper.qmd
Fixed Figure 7

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 15

@@

```{r}
#| label: hexbin-regular-two-curvy2
## hexagon binning to have regular hexagons
hb_obj_two_curvy2 <- hex_binning(
  data = tsne_two_curvy_scaled, 
  bin1 = 23, 
  r2 = r2)

a1_2 <- calc_bins_y(
  bin1 = 23, 
  r2 = r2
  )$a1

@@

hex_grid_coloured_two_curvy1 +
  hex_grid_coloured_two_curvy2 +
  hex_grid_coloured_two_curvy3 +
  plot_layout(guides='collect', ncol = 3) &
  theme(legend.position='none', plot.tag = element_text(size = 8))
```

>>>>

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 23

@@

```{r}
#| label: hexbin-regular-two-curvy2
## hexagon binning to have regular hexagons
hb_obj_two_curvy2 <- hex_binning(
  data = tsne_two_curvy_scaled, 
  bin1 = 15, 
  r2 = r2)

a1_2 <- calc_bins_y(
  bin1 = 15, 
  r2 = r2
  )$a1

@@

hex_grid_coloured_two_curvy2 +
  hex_grid_coloured_two_curvy1 +
  hex_grid_coloured_two_curvy3 +
  plot_layout(guides='collect', ncol = 3) &
  theme(legend.position='none', plot.tag = element_text(size = 8))
```
